article title

### 2022-07-23 pilon_gilles_glossary.tex
Revise confidence interval

    description={It is an interval calculated from values in a sample. The interval is constructed for a specified probability of containing the unknown true value of a population parameter.

>>>>

    description={In frequentist statistics, it is a range of estimates for an unknown parameter, interval calculated from values in a sample.
